Kernel Development Using Rust: A Systematic Literature Review

### 2024-05-03 paper.tex
Update on Overleaf.
Added cttc for paper review

\begin{document}
\title{Rust for Operating System Development: A Systematic Literature Review}

@@

Following the guidelines outlined by Kitchenham and Charters~\cite{Stuart2007-cc} we set the
inclusion and exclusion criteria based on our research questions outlined in
section~\ref{sec:researchQuestions}. We only consider papers that are written in English, published
in conferences or journals, and within the time frame of 2019 and 2024. The published papers should
describe using the Rust programming language for either developing a new kernel, extending an
existing kernel, or authoring drivers. We will include any type of kernel architecture including
monolithic, micro, or uni as long as the paper is using the Rust programming language.

@@

\subsection{RQ1}
\subsection{RQ2}
\subsection{RQ3}

>>>>

\begin{document}
\title{Kernel Development Using Rust: A Systematic Literature Review}
%\title{}

@@

Following the guidelines outlined by Kitchenham and Charters~\cite{Stuart2007-cc} we set the
inclusion and exclusion criteria based on our research questions outlined in
section~\ref{sec:researchQuestions}. We only consider papers that are written in English, published
in conferences or journals, and within the time frame of 2019 and 2024. The published papers should
describe using the Rust programming language for either developing a new kernel, extending an
existing kernel, or authoring drivers. We will include any type of kernel architecture including
monolithic kernel, microkernel, or unikernel in both the embedded and non-embedded space as long as
the paper is using the Rust programming language in some way.

@@

\begin{table}
  \begin{tabular}{||c|c||}
    \hline
    System Type & Papers\\
    \hline\hline
    Embedded & ~\cite{Ayers2022-vk} \\
    Non-Embedded & 0 \\
    Unikernel & 0 \\
    Kernel & 0 \\
    \hline
  \end{tabular}
\end{table}

This is a list of operating systems.
\begin{itemize}
\item \href{https://docs.kernel.org/rust/}{Linux kernel v6.1+}
\item \href{https://github.com/tock/tock}{Tock}
\item \href{https://hubris.oxide.computer/}{Hubris OS}
\item Theseus
\end{itemize}
